Methods for Large Scale Learning to Rank

### 2014-03-05 report/Chapters/Introduction.tex
introduction sterker gemaakt

%********************************************************************
% Appendix
%*******************************************************
% If problems with the headers: get headings in appendix etc. right
%\markboth{\spacedlowsmallcaps{Appendix}}{\spacedlowsmallcaps{Appendix}}
\chapter{Motivation and Problem Statement}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance for a given query. Ranking is useful in many other application domains outside information retrieval as well, amongst others in drug discovery and to determine the order of maintenance operations \cite{Rudin2009}. Learning-to-Rank has also been argued to be a more fitting approach to recommender systems than rating prediction \cite{Adomavicius2005,McNee2006}.\\

>>>>

%********************************************************************
% Appendix
%*******************************************************
% If problems with the headers: get headings in appendix etc. right
%\markboth{\spacedlowsmallcaps{Appendix}}{\spacedlowsmallcaps{Appendix}}
\chapter{Motivation and Problem Statement}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance for a given query. Ranking has become a vital part of web search, where commercial search engines help users find their need in the extremely large collection of the World Wide Web. One can find useful applications of ranking in many application domains outside web search as well. For example, it plays a vital role in amongst others: document summarisation, machine translation, drug discovery and in determining the ideal order of maintenance operations \cite{Rudin2009}. In addition, the ranking task has been argued to be more fitting to recommender systems than rating prediction on a continuous scale \cite{Adomavicius2005,McNee2006}.\\
